paper2_resistance_mechanisms_mixtures

### 2017-02-21 inst/documents/paper2/paper2_resistance_mechanisms_mixtures.Rmd
add fig 1

![New figure showing how fitness determined by inputs](paper2_mod_graphic_a_to_c.png)

@@

```{r Fig8, eval=FALSE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', fig.cap="A. All control inputs equal at 0.5, male exposure 0.8, B. Effectiveness for insecticide1 increased from 0.5 to 0.8, C. Male exposure decreased from 0.8 to 0.2, D. Effectiveness for insecticide1 increased from 0.5 to 0.8 and Male exposure decreased from 0.8 to 0.2"}

>>>>

```{r Fig1, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=7.5, fig.width=7.5, fig.show='hold', fig.align='left', fig.cap="Diagrammatic representation of the effect of model inputs on the fitness of genotypes for a single insecticide. Fitness is shown on the y-axis and the different genotypes (SS, SR, RR) on the x axis. Firstly the exposure input determines the proportion of the population in the left and right panels (exposed and not exposed). For those that are exposed (left panel) insecticide effectiveness sets the fitness for SS, resistance restoration 'restores' a portion of the fitness for RR and dominance determines how the fitness for SR sits between that of SS and RR. For those that are not exposed, fitness of SS is set to 1 by definition, resistance cost determines the fitness of RR and again dominance determines how the fitness for SR sits between that of SS and RR. In this example effectiveness=0.8, dominance=0.5, resistance restoration=0.5 and resistance cost=0.3."}

plot_fit_calc( effectiveness=0.8, resistance_restoration=0.5, dominance=0.5, cost=0.3 )

@@

```{r Fig9, eval=FALSE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', fig.cap="A. All control inputs equal at 0.5, male exposure 0.8, B. Effectiveness for insecticide1 increased from 0.5 to 0.8, C. Male exposure decreased from 0.8 to 0.2, D. Effectiveness for insecticide1 increased from 0.5 to 0.8 and Male exposure decreased from 0.8 to 0.2"}
